Hypercoercions and a Framework for \\ Equivalence of Cast Calculi

### 2020-01-16 paper.tex
change header

%% For double-blind review submission, w/o CCS and ACM Reference (max

%%submission space)
\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max 
%%submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2020}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

>>>>

\documentclass[acmsmall,screen]{acmart}\settopmatter{printacmref=true}
\acmConference[WGT20]{ACM SIGPLAN Workshop on Gradual Typing}{January 25,
	2020}{New Orleans}
\acmBooktitle{Informal Proceedings of the first ACM SIGPLAN Workshop on
	Gradual Typing (WGT20)}
\acmDOI{}
\acmPrice{}
\setcopyright{none}
%
%%% For double-blind review submission, w/o CCS and ACM Reference (max 
%
%%%submission space)
%\documentclass[acmsmall]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%%% For double-blind review submission, w/ CCS and ACM Reference
%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%%% For single-blind review submission, w/o CCS and ACM Reference (max 
%%%submission space)
%%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%%% For single-blind review submission, w/ CCS and ACM Reference
%%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%%% For final camera-ready submission, w/ required CCS and ACM Reference
%%\documentclass[acmsmall]{acmart}\settopmatter{}
%
%
%%% Journal information
%%% Supplied to authors by publisher for camera-ready submission;
%%% use defaults for review submission.
%\acmJournal{PACMPL}
%\acmVolume{1}
%\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
%\acmArticle{1}
%\acmYear{2020}
%\acmMonth{1}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}
%
%%% Copyright information
%%% Supplied to authors (based on authors' rights management selection;
%%% see authors.acm.org) by publisher for camera-ready submission;
%%% use 'none' for review submission.
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear
